Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-12-17 lloveras_2020.tex
mas texto, correcciones por aca y por alla

\address[id=aff3]{Facultad de Ciencias Exactas y Naturales (FCEN), Universidad de Buenos Aires (UBA), Pabell\'on II, Ciudad Universitaria, (C1428ZAA) Ciudad Aut\'onoma de Buenos Aires, Argentina}

@@

@@

\begin{equation}\label{Er}
E_r = \int\,\Lambda(T)\,dN_e^2(T).
\end{equation}

@@

As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr \Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$. As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height may be used to compute the tomographic basal electron density at $\sqravgN(r=1.025\,\mrsun)$ as in previous articles. In this case, for further comparison analysis with the AWSoM results, we selected the lowest height where the results of the MHD model are reliable, that is $1,055\,\mrsun$.

@@

As a way of knowing the physical position of the types of lines defined in Section \ref{trace}, the Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations. In cyan the type 0 lines are indicated, populating the most equatorial latitudes (dominated mostly by down loops). This kind of structures has been informed in previous works, \citet{lloveras_2017} observed down {loops} in a rotation during the solar minima of 1996 and for the previous rotation CR-2081. A decrease in the amount of down loops in equatorial latitudes could be an indicator of increased coronal activity \citet{nuevo_2013}. In blue the type 1 lines, populating all the streamer but mostly the mid latitudes. In red the type 2 lines, are mostly very large trans-equatorial field lines forming the envelope of the Streamer belt, and in green dots the type 3 lines, populating the coronal holes.

@@

To compare obtained traced results in both rotations and for each type of lines (associated with differents types of regions), Figure \ref{gradt_demt} shows histograms (normalized to the total amount of the field lines selected) of the temperature radial gradients ($\dr \Tm$). The lack of population around values close to zero is due to the strict condition $|\rho_t| > 0.5$ that discards possible isothermal values, according to DEMT results.

@@

As an example of the traced magnitudes, Figure \ref{histos_fulldemt} shows the statistical results of both rotations for all field lines types. From top to bottom type 0 to type III. From left to right the panels show the statistical distribution of $\NCB$, $\lN$, $\aTm$, in each panel the median $m$ is indicated.

@@

To compare integrated quantities along loops, we select those close loops where both legs meet the requirements of Section \ref{trace}. In an analogous way to the legs definition, we will refer to them as loops of type 0, I or II.

@@

The type I loops show a loop-integrated positive conductive for each loop in both rotations consistent with positive gradients of temperatures. \diego{We found larger temperature gradients for CR2208 than CR2082 (SI?)}, but for the most population of loops, the conductive flux have values around 0.3 $10^{5}[\rm{erg\,sec^{-1}\,cm^{-2}}]$ in both rotations. Similar results have been found for loop-integrated radiative flux and energy input flux for both rotations.

Type 0 loops present larger gradients than type I. Therefore, type 0 present bigger amount, in modulus, of loop-integrated conductive flux. Due conductive flux negative can not be assumed as a loss but it can be contributing to the coronal heating. Thus, to compensate the radiative losses, a lower loop-integrated energy input flux is required.

@@

@@

The actual version of the AWSoM model can not reproduce down loops, so for a further comparison we only select lines of type 1, 2 and 3 of those meeting the criteria described in Section \ref{trace}.
As a way to understand the distribution of the selected lines, Figure \ref{rpoint_awsom} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations. In blue the type 1 lines, populating mostly the entire streamer. In red the type 2 lines, populating the edge that assemble the envelope around the streamer, and in green dots the type 3 lines, populating the coronal holes.

The reader may notice that these structures are the same as those in Figure \ref{rpoint_demt} but more filled, the cause is twofold. On the one hand the same magnetic model was used to trace both DEMT and AWSoM results, on the other hand is because giving the model smoother results, fewer fitted lines are filtered.

\begin{figure}[h!]
\begin{center}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.pdf}
\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its loops in types I, II and III. The model does not exhibit loops of type 0.}}
\label{rpoint_awsom}
\end{center}
\end{figure}

@@

\diego{
*awsom da valores mas altos en los polos\\
*Parece haber una buena coincidencia en CR2082 en Te yen CR2208 en Ne.\\
*En CR2082 en Ne demt es 20 \% mas grande que awsom en la zona cerrada.\\
*En cr2208 en Te, en la zona polar awsom es 30\% mas grande y awsom es 25\% mas grande en la region cerrada.
}

@@

To summarize the comparison between both results during both rotations at full height, it is shown in Figure \ref{perfiles_promedio} the average fits of $\Ne(r)$ and $T_e(r)$ for every type of legs.

\diego{Explicar lo que se observa:
- Ne 1.65 awsom menor que la de demt en CR2082 y mayor que la de CR2208 y debido a que decaen esponencialmente, el hecho que tiendan a valores similares conforme aumenta la altura implica escalas de altura similares. \\
- Las temperaturas a 1.065 difieren en ambas rotaciones y en todas las regiones/tipos de lineas siendo siempre menor la de awsom, sin embargo las pendientes son similares en todas la regiones. Excepto que los gradientes de cr2208 en CH son mayores demt consistente con la fig de grad de temp, me preg si esto es por AIA.}

@@

As way of example, Figure \ref{histos_2082} and \ref{histos_2208} shows the statistical results of both rotations for the three types of field lines traced with DEMT (blue) and AWSoM results (red). From left to right the panels show the statistical distribution of $\NCB$, $\lN$ and $\aTm$. For all types of lines, Table \ref{tabla_comp} summarizes the median value of the statidtical distribution of each physical quantity derived from the analysis. The DEMT quantities are expressed as absoulte values, while for ASWSoM they are informed relative to the corresponding result for DEMT.

\diego{comentar lo que se desprende de los graficos y la tabla.}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
\caption{{Statistical distribution of DEMT (blue) and AWSoM (red) results traced along legs of type I, II and III (from top to bottom), as defined in Section 2.3. From left to right: electron density at the coronal base $\NCB\equiv \Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$. In each panel the median value $m$ is indicated.}}
\label{histos_2082}
\end{center}
\end{figure}

%For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were separated into the coronal {regions described in Section \ref{regions} and summarized in Table \ref{tabregions}}. For each field line, the data points of electron density and electron mean temperature versus height were fitted to the functions given by Equations 5 and 6 of Section \ref{trace}. As a result, the footpoint electron density $N_0$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $a=\textrm{d}\Tm/\textrm{d}r$, and the height-averaged (along the loop) electron mean temperature $\aTm$. As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data versus height was used to compute the {coronal base electron density} here defined as $\NCB\equiv \Ne(r=1.025\,\mrsun)$. Also, for each field line the coronal base magnetic field strength $B_{\rm CB}\equiv B(r=1.025\,\mrsun)$ and its height-averaged value along the loop $\left<B\right>$ were also computed.

@@

This effect can be due a subestimation of the density present in the loop or the limited range of temperature used to reconstruct tomographic parameters, that can affect the compute of radiative power. Nevertheless, this population represent lower than the \diego{ALGÚN PORCENTAJE$\%$} of total population in both cases.  Bottom panels show the comparison for larger type I loops. We observe similar median values for the three loop-integrated energy quantities for both rotations.

>>>>

\address[id=aff3]{Ciclo Básico Común (CBC), Universidad de Buenos Aires (UBA), Buenos Aires, Argentina}

@@

%correcciones a hacer! DIEGO
%Los términos de la Eq (10) requieren ser explicados. La explicación a conituación no es clara, y de hecho está mal escrita. La Eq. (7) se integra en el VOLUMEN CORONAL COMPLETO de cada tubo de flujo y se divide por el área basal del mismo. Utilizando la condición solenoidal de B se llega a la Eq. (7), dónde... y ahí deberían darse las expresiones de Phir y Phic porque no pertenecen a la literatura estandard, y explicar a continuación como todos los elementos de esas dos expresiones surgen de los fits de DEMT y del modelo magnético de AWSoM. Donde si se puede ahorrar mucho espacio es en lo previo, la Eq (8) podría no incluirse por ejemplo. Creo que ahora lo mejor es que trates de completar la explicación dando las expresiones de Phir y Phic, y luego vemos de como limarla, probablemente eliminando la ec. (8). y además el texto puede compactarse, corregirse y reordenarse mucho. Poné las unidades de las cantidades Phi entre paréntesis a continuación de $\Phi_{h,r,c}$.

@@

\begin{equation}\label{Er}
E_r = \int\,\textrm{d}T\,T\,\LDEM(T)\,\Lambda(T)
\end{equation}

@@

As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr \Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$. As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height may be used to compute the tomographic electron density at the coronal base $\sqravgN(r=1.025\,\mrsun)$ as in previous articles. In this case, for further comparison analysis with the AWSoM results, we selected the lowest height where the results of the MHD model are reliable, that is $1,055\,\mrsun$.

@@

As a way of knowing the physical position of the types of lines defined in Section \ref{trace}, the Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations. In cyan the type 0 lines are indicated, populating the most equatorial latitudes (dominated mostly by down loops). This kind of structures has been informed in previous works, \citet{lloveras_2017} observed down {loops} in a rotation during the solar minima of 1996 and for the previous rotation CR-2081. A decrease in the amount of down loops in equatorial latitudes could be an indicator of increased coronal activity \citet{nuevo_2013}. In blue the type I lines, populating all the streamer but mostly the mid latitudes. In red the type II lines, are mostly very large trans-equatorial field lines forming the envelope of the Streamer belt, and in green dots the type III lines, populating the coronal holes.

@@

To compare obtained traced results in both rotations and for each type of lines (associated with differents types of regions), Figure \ref{gradt_demt} shows histograms (normalized to the total amount of the field lines selected) of the temperature radial gradients ($\dr \Tm$). The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs.

@@

As an example of the traced magnitudes, Figure \ref{histos_fulldemt} shows the statistical results of both rotations for all field lines types. From top to bottom type 0 to type III. From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$, $\lN$, $\aTm$, in each panel the median $m$ is indicated.

@@

To compare integrated quantities along loops, we select those close loops where both legs meet the requirements of Section \ref{trace}. In an analogous way to the legs definition, we will refer to them as loops of type 0, I or II to those whose both legs meeting the criteria. Now the type 0 loops are down loops.

@@

Type 0 loops present slightly larger gradients than type I. Therefore, type 0 present bigger amount, in modulus, of loop-integrated conductive flux. Due conductive flux negative can not be assumed as a loss but it can be contributing to the coronal heating. Thus, to compensate the radiative losses, a lower loop-integrated energy input flux ($\phi_h$) is required.

@@

The type I loops show a loop-integrated positive conductive for each loop in both rotations consistent with positive gradients of temperatures. The differences

We found larger temperature gradients for CR2208 than CR2082, but for the most population of loops, the conductive flux have values around 0.3 $10^{5}[\rm{erg\,sec^{-1}\,cm^{-2}}]$ in both rotations. Similar results have been found for loop-integrated radiative flux and energy input flux for both rotations.

@@

The actual version of the AWSoM model can not reproduce down loops, so for a further comparison we only select lines of type I, II and III of those meeting the criteria described in Section \ref{trace}.
As a way to understand the distribution of the selected lines, Figure \ref{rpoint_awsom} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations. In blue the type I lines, populating mostly the entire streamer. In red the type II lines, populating the edge that assemble the envelope around the streamer, and in green dots the type III lines, populating the coronal holes.

The reader may notice that these structures are the same as those in Figure \ref{rpoint_demt} but more filled. The cause is twofold, on the one hand the same magnetic model was used to trace both DEMT and AWSoM results, on the other hand is because giving the model smoother results, fewer fitted lines are filtered.

\begin{figure}[h!]
\begin{center}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.pdf}
\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify {its legs in types I, II and III. The model does not exhibit legs of type 0.}}
\label{rpoint_awsom}
\end{center}
\end{figure}

@@

According to the visual inspection on the maps of carrington, the latitudinal profiles comparing both DEMT and AWSoM results are on the same scale. Little difference in density is observed in CR-2208 and in temperature in CR-2082, while DEMT in CR-2082 was $20\%$ denser. Finally, DEMT results for CR-2208 were $25\%$ hotter in the streamer and $30\%$ colder in the polar zone than AWSoM.
Density profiles on AWSoM show an increase around the polar zone, which seems like an artifice.

@@

To summarize the comparison between both results during both rotations at full height, it is shown in Figure \ref{perfiles_promedio} the average fits of $\Ne(r)$ and $T_e(r)$ for legs of type I (blue), II (red), and III (green) for both rotations.

In average all temperature and density behavior from both results are on the same scale.
The coronal base densities of AWSoM were lower than those of DEMT in CR-2082 and higher in CR-2208. The fact that the density decays to similar values between both results suggests a similar height scale. Onthe other hand basal temperature of AWSoM was lower in both rotations, but the temperature gradients are very similar en each type of legs, showing a very similar increase of temperature with height.

@@

Tu summary the statistical comparison, Figure \ref{histos_2082} and \ref{histos_2208} shows the statistical results of both rotations for the three types of field lines traced with DEMT (blue) and AWSoM results (red). From left to right the panels show the statistical distribution of $\NCB$, $\lN$ and $\aTm$. For all types of lines, Table \ref{tabla_comp} summarizes the median value of the statidtical distribution of each physical quantity derived from the analysis. The DEMT quantities are expressed as absoulte values, while for ASWSoM they are informed relative to the corresponding result for DEMT.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
\caption{{Statistical distribution of DEMT (blue) and AWSoM (red) results traced along legs of type I, II and III (from top to bottom), as defined in Section 2.3. From left to right: electron density at the coronal base $\NCB\equiv \Ne(r=1.055\,\mrsun)$\diego{en realidad Ncb se define distinto para awsom que demt.}, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$. In each panel the median value $m$ is indicated.}}
\label{histos_2082}
\end{center}
\end{figure}

@@

This effect can be due a subestimation of the density present in the loop or the limited range of temperature used to reconstruct tomographic parameters, that can affect the compute of radiative power. Nevertheless, this population represent lower than the \diego{ALGÚN PORCENTAJE$\%$} of total population in both cases.  Bottom panels show the comparison for larger type I loops.
